Practical Machine Learning Project Work - Weigh Lifting Dataset
========================================================

# Backgroud



## Environment

We first intialize the environment by included the libraries used and by setting the seed for random number generator.

```{r}
setwd("D://")
require(dplyr)
require(caret)
library(e1071)
library(adabag)
set.seed(1314)
```

## Data processing


- train_data is the training data set
- test_data is the test set

```{r}
train_data <- read.csv("pml-training.csv")
test_data <- read.csv("pml-testing.csv")
```

We should clean the data first.

```{r}
near_zeros <- nearZeroVar(train_data[,-160])
train_data_cleaned <- train_data[, -near_zeros]
test_data_cleaned <- test_data[, -near_zeros]
```

Deleting the missing data

```{r}
has_nas <- colSums(is.na(train_data_cleaned)) > 0
train_data_cleaned <- train_data_cleaned[, !has_nas]
test_data_cleaned <- test_data_cleaned[, !has_nas]
```

```{r}
train_data_cleaned <- train_data_cleaned[, 7:59]
test_data_cleaned <- test_data_cleaned[, 7:59]
```


## Creating data sets for cross-validation



```{r}

in_train <- createDataPartition(train_data_cleaned$classe, p = 0.7, list=FALSE)
training <- train_data_cleaned[in_train, ]
testing <- train_data_cleaned[-in_train, ]

```

## Prediction with SVM


```{r, cache=TRUE}
a=svm(classe~.,data=training,kernal="sigmoid")
z0=table(training[,53],predict(a,training))
z0
```
The accuracy of the model (out ot sample) is 94.95%
## Prediction with randomForest
.

```{r,cache=TRUE}
b=randomForest(classe~.,data=training, method="class")
z1=table(training[,53],predict(b,training))
z1
```
 The accuracy of the model (out ot sample) is 100
 Therefore, we chose randomForest to predict test data.

```{r}
real_preds <- predict(b, newdata=test_data_cleaned)
```

And finally write them to a file with a function provided in the project.

```{r}

# function for writing the output files
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

# write the predictons generated in the previsou step into files.
pml_write_files(real_preds)
```




